\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-12 paper/paper.tex
Work on intro, remove redundant bibtex entry

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Failure data for series systems may be collected at the system level by end-users interested only in the lifetime of the system. In the case of complex, high-reliability systems where cause of failure is not available, a model of failure which
\begin{enumerate}[a]
\item can be estimated from the observed data
\item is flexible enough to fit the observed data
\item relies on an approximation of the understood underlying process
\end{enumerate}
is desirable. We present a Bayesian, hierarchical modeling approach for grouped failure data. We demonstrate this approach with a large, heavily censored real data set with multiple right-censoring and left truncation times. We extend the generalized limited failure population model (GLFP) by \citet{chan}, which provides a generative model for failure times in a population with infant mortality. This model is an example of a bathtub distribution, exhibiting distinct early and late failure modes. The GLFP model assumes there are two causes of failure, one of which affects only a fraction of the population, and that the cause of failure is unobserved. We extend this model to grouped data and show that by borrowing information across groups we can achieve good model fits for almost all groups. By working with posterior samples, we can easily make inference on a wide range of quantities of interest while accounting for uncertainty.

>>>>

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Failure distributions of high-reliability products, can be difficult
to assess. Accelerated testing tries to address this problem, but
requires strong assumptions to extrapolate to use conditions in the
field (citation). When field data are available, information may be
very limited. In this paper, we propose the use of Bayesian hierarchical modeling to borrow
information to improve inferences on lifetime
distributions where information is limited by right-censoring and
left-truncation.

Failure data for series systems may be collected at the system level
by end-users interested only in the lifetime of the system. \citet{chan} proposed the generalized limited failure population
model (GLFP), which provides a generative model for
failure times in a population where some units are susceptible to infant mortality. This model
covers a subset of the class of distributions known as bathtub distributions
\cite{sujata}. Bathtub distributions are characterized by a U-shaped
hazard function, where early failures are due to infant mortality and
late failure are due to wearout. While complex systems actually
exhibit more than two modes of failure, suitable parametric models
which can suitably approximate the overall lifetime distribution are
useful.

In the case of complex, high-reliability systems where cause of failure is
not available, a model which
\begin{enumerate}[a.]
\item has parameters that can be estimated from the observed data
\item is flexible enough to fit the observed data
\item in interpretable with respect to available theory of the underlying process
\end{enumerate}
is desired. We present a Bayesian, hierarchical modeling approach for
grouped failure data. As a benefit of working with Monte Carlo
samples, we can easily make inference on a wide range of quantities of
interest while accounting for uncertainty. We demonstrate this approach on real data hard
drive failure data from a
cloud-based storage company.
